### 2017-06-15 manuscript/manuscript.Rmd
Clarify Git & GitHub configuration

To operate properly, Git needs to be able to identify its user. You can set these by entering a few basic commands in the Terminal. The following commands are intended to be entered to Terminal or a similar command line interface. To verify the current user information, type `git config --global user.name`, and hit return. This should not return anything, unless a previous user of the computer has set the global Git user name.

To ensure that Git knows who you are, type `git config --global user.name "User Name"` (where User Name is your name), and hit return. If you now re-run the first command, Terminal will return the name you entered as `"User Name"`. The second piece of information is your email, which can be entered by `git config --global user.email "email@address.com"` (where email@address.com is your email address). You can verify that the correct email address was saved by typing `git config --global user.email` in the Terminal, and hit return. Once this information is entered, Git will know who you are, and is thus able to track who is doing what within a project, which is especially helpful when you are collaborating with other people, or when you are working on multiple computers.

@@

@@

Anyone wanting to use GitHub must first create a free user account at <https://github.com>. After the user account has been set up, and the user has logged in, creating a new repository at GitHub is self evident (there is a big green button labeled "New repository").

>>>>

@@

## Git setup

To operate properly, Git needs to be able to identify its user. You can set these by entering a few basic commands in the command line. To verify the current user information, type `git config --global user.name`, and hit return. This should not return anything, unless a previous user of the computer has set the global Git user name.

To ensure that Git knows who you are, type `git config --global user.name "User Name"` (where User Name is your name) in the command line, and hit return. If you now re-run the first command, the command line will return the name you entered as `"User Name"`. The username can be anything you'd like, but it is probably a good idea to use your real name so that potential collaborators know who you are. The second piece of information is your email, which can be entered by `git config --global user.email "email@address.com"` (where email@address.com is your email address). You can verify that the correct email address was saved by typing `git config --global user.email` in the Terminal, and hit return. Once this information is entered, Git will know who you are, and is thus able to track who is doing what within a project, which is especially helpful when you are collaborating with other people, or when you are working on multiple computers.

@@

Anyone wanting to use GitHub must first create a free user account at <https://github.com>. After the user account has been set up, and the user has logged in, creating a new repository at GitHub is self evident (there is a big green button labeled "New repository"). You must create the GitHub account with the same email address as you used above when configuring your local Git (or re-configure your local Git to use your the email address that you used to register for GitHub).
